\begin{frame}{Hall's Theorem}
A bipartite graph G consisting of sets U and W, has a matching satisfying $|u|$ if and only if $|N(x)| \geq |x|$ for every nonempty subset X of U.
  
\end{frame}

\begin{frame}{Example 1 - Hall's Theorem}
Does G have a matching of size 5?
-- Example on the Board -- 
\end{frame}

\begin{frame}{Solution 1 - Hall's Theorem}
No, because: Let $X = {B,C}$. $N(x) = {3}$. $|N(x)| = 1$, $|x| = 2$. Violates Hall’s Condition.
  
\end{frame}

\begin{frame}{Example 2 - Hall's Theorem}
Does G have a matching of size 5?
 -- Example on the Board -- 
\end{frame}

\begin{frame}{Solution 2 - Hall's Theorem}
No, because: Let $X = {B,C,D}$. $N(x) = {1,3}$. $|N(x)| = 2$, $|x| = 3$. Violates Hall’s Condition.
  
\end{frame}

\begin{frame}{Example 3 - Hall's Theorem}
Does G have a matching of size 4?
-- Example on the Board -- 
\end{frame}

\begin{frame}{Solution 3 - Hall's Theorem}
Yes. ${C4, D3, A2, B1}$. 
  
\end{frame}
  
\begin{frame}{Königs Theorem}
The maximum matching for a bipartite graph equals its minimum vertex cover
  
\end{frame}

\begin{frame}{Königs Theorem - Example}
-- Example on the Board -- 
  
\end{frame}

\begin{frame}{Alternating Path}
Let $G = (X, Y, E)$ be a bi-partite graph where the vertices are divided into the sets X and Y and E the edges.
  
\end{frame}

\begin{frame}{Alternating Path}
-Picture-
  
\end{frame}

\begin{frame}{Alternating Path}
-Picture-
  
\end{frame}

\begin{frame}{Alternating Path - Summary}
- An alternating path will start in a vertex element of X and ends in vertex element of Y
- An alternating path must have an odd-number of edges
- An alternating path will visit nodes in X und Y alternatedly

-> To go forward, use an edge that is not part of the matching
-> To go backward, use an edge that is part of the matching
  
\end{frame}

\begin{frame}{Augmenting Path - Definition}
Given a matching M, an alternating path is a path where edges are alternately in M and not in M. An augmenting path is an alternating path where the first and last vertex are unmatched.
  
\end{frame}

\begin{frame}{Augmenting Path - example}
-on the board-
  
\end{frame}

\begin{frame}{Breadth First Search - repetition}
-on the board-
  
\end{frame}

\begin{frame}{Berge Theorem}
A matching is a maximum matching iff it contains no augmenting path.
  
\end{frame}

\begin{frame}{Hungarian Method}
we search augmenting paths in the graph until no augmenting path can be found. Using Berge Lemma, our matching is Maximum
\end{frame}

\begin{frame}{Maximum Flow Reduction}
-on the board-
  
\end{frame}

\begin{frame}{Hopcraft-Carp Algorithm}
Initialize Matching Empty 
Repeat
	Build alternating level graph rooted at unmatched vertices in L using bfs.
	Augment M via maximal set of vertex disjoint shortest-length paths
	until no augmenting paths exists
	Return M
		
Time complexity: O(|E|)
  
\end{frame}

\begin{frame}{Hopcraft-Carp Algorithm - bipartite Graph}

-example on the board-
  
\end{frame}

\begin{frame}{Hopcraft-Carp Algorithm - non-bipartite Graph}

-example on the board-
  
\end{frame}